### 2014-08-07 Docs/mg/mg.tex
bndry_reg corrections from the boxlib docs

A \bndryreg\ is a set of {\tt dim*2} multifabs defined on the coarse cells
immediately outside of each fine grid.

Ideally we would only include the cells not covered by a different
fine grid, but in the current implementation, for {\tt N} fine grids we have
{\tt N*dim*2} multifabs (the factor of 2 is {\tt lo}/{\tt hi}).

We use the \bndryreg to store the correction to the residual to be
used in the coarse grid relaxation.  The way we use it is that we
compute a pure coarse grid residual in every coarse cell, then we
correct it by subtracting the contribution of the coarse flux under
the coarse-fine edge and adding the contribution of the fine fluxes at
that same interface.  The \bndryreg\ holds the cell-centered
contribution from the difference of these edge fluxes and is added to
the coarse residual multifab.

>>>>

There are two types of \bndryreg\ objects, each of which is a set of
{\tt dim} multifabs.  The first, which is built with the {\tt
bndry\_reg\_build} call, is defined on all cells immediately outside
of each grid.  Each multifab within the \bndryreg\ contains all the
fabs on both the low and high faces for a given direction.  In the
context of multigrid, we fill the \bndryreg\ with coarse data before
interpolating the data to the correct locations to be used in the
multigrid stencil.  The second type of \bndryreg\ object is defined on
the coarse cells immediately outside each fine grid, and is defined
with the {\tt bndry\_reg\_rr\_build} call, is defined on all cells
immediately outside.  For this latter type, the option is available
to include only cells not covered by a different fine grid, but this
is left as an option because it requires additional calculations of
box intersections.

In multigrid, we use the latter type of \bndryreg\ to calculate the
residual at coarse cells adjacent to fine grids that is used as the
right hand side in the relaxation step at the coarse level on the way
down the V-cycle (or other).  The first type of \bndryreg is used to
hold boundary conditions for the fine grids that are interpolated from
the coarse grid solution; this is filled on the way back up the
V-cycle.

To compute the residual in a coarse cell adjacent to a fine grid, we
first compute the pure coarse residual, then subtract the contribution
from the coarse face underlying the coarse-fine interface, and add the
contribution of the fine faces at the coarse-fine interface.
The \bndryreg\ holds the cell-centered contribution from the
difference of these edge fluxes and is added to the coarse residual
multifab.
